---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/hottopic.svg?branch=master)](https://travis-ci.org/hrbrmstr/hottopic) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/hottopic/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/hottopic)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/hottopic)](https://cran.r-project.org/package=hottopic)

# hottopic

Retrieve Hot Topics (Trends) for a Given Country from 'Google' Trends

## Description

Retrieve Hot Topics (Trends) for a Given Country from 'Google' Trends

## What's Inside The Tin

The following functions are implemented:

- `get_topic`:	Retrieve Hot Topics (Trends) for a Given Country
- `topic_countries`:	Return a character vector of supported countries

## Installation

```{r install-ex, eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/hottopic.git")
# or
devtools::install_github("hrbrmstr/hottopic")
```

## Usage

```{r lib-ex}
library(hottopic)
library(tibble) # for printing

# current version
packageVersion("hottopic")

```

### Countries

```{r ccs}
topic_countries()
```

```{r topics}
get_topic()
```

## hottopic Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
